---
title: "My first R package"
author: "Antonio Domingues"
date: "January 1, 2018"
output: html_document
---

My first R package

Installed usethis to automate some of the task.

```{r include=FALSE}
devtools::install_github("r-lib/usethis")
library(usethis)
setwd("/home/adomingu/sandbox")
pkg_dir <- file.path(".", "cleaneRnames")
create_package(pkg_dir)
```

I choose the license "MIT" because straight and to the point.

```{r}
use_mit_license("António Domingues")
```

Then in Rstudio I just opened the project created by `usethis`.

Importantly I need some code for it. 

```{r }
use_readme_md()
```

And set-up of the GH repo:

```{r }
use_git()
```

build from the command-line:

```{r }
library(devtools)
setwd(pkg_dir)
build()
install()
```

And then we create the documentation.

```{r docs}
document()
```

It seems like the package `janitor` already [does](https://garthtarr.github.io/meatR/janitor.html) something similar, but I will continue anyway to practice R package creation.


I should consider adding a [test](https://4dpiecharts.com/2011/07/04/testing-for-valid-variable-names/#comments) for syntactically valid names. 